%-------------------------
% Nicolo DiFerdinando Resume
% Author : Nicolo DiFerdinando
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeCampusInvolvement}[3]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}, #2 & #3 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING-----------------
\begin{center}
  \textbf{\Huge \ \scshape Nicolo DiFerdinando} \\ \vspace{3pt}
   \href{mailto:ndiferdi@calpoly.edu}{ndiferdi@calpoly.edu} $|$ \small 949-274-0390 $|$ \href{https://www.nicolod.org}{nicolod.org} $|$ \href{https://www.linkedin.com/in/nicolo-diferdinando/}{linkedin.com/in/nicolo-diferdinando/} $|$ \href{https://www.https://github.com/nicodiferd}{https://github.com/nicodiferd}

\end{center}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California Polytechnic State University, San Luis Obispo}{San Luis Obispo, CA}
      {Bachelor of Science in Industrial Engineering}{Sept. 2021 -- June. 2026}\\[3mm]
      \textbf{Relevant Coursework:} Data Science, Data Analytics, Data Management and System Design, Operations Research, Design and Manufacturing, Statistics for Engineering, Machine Learning\\
      \textbf{Engineering Test Design and Analysis:} Curated optimization strategies for workflow and deployment\\
      \vspace{2pt} % Add vertical space here
      \textbf{Certifications:} Splunk Core Certified User
      \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cal Poly San Luis Obispo}{San Luis Obispo, CA}
      {Assistant Student SOC Analyst}{2024-Current}
      \resumeItemListStart
        \resumeItem{Cybersecurity Response}
          {Analyze and respond to suspicious logins, phishing emails, and network traffic using Splunk Enterprise to mitigate threats.}
        \resumeItem{Python-based Slack Automation}
          {Created a Python-based Slack application to automate tasks such as email confirmation, suppression, and blocking procedures.}
        \resumeItem{Splunk Soar Integration}
          {Integrated Splunk Soar Playgrounds, SSH commands to block and suppress users, and Slack Bolt APIs to get button and modal interactivity.}
      \resumeItemListEnd

    \resumeSubheading
      {loanDepot}{Irvine, California}
      {Cyber Security Intern}{2022}
      \resumeItemListStart
        \resumeItem{Cyber Threat Intelligence}
          {Aided in the Cyber Intelligence team's threat prioritization based on incoming threat intelligence (actor-based and behavior/tactic-based).}
        \resumeItem{Incident Investigations}
          {Assisted members of Cyber Operations teams (SOC and CIRT) in incident investigations, requiring intelligence assistance.}
        \resumeItem{Security Compliance Audits}
          {Performed compliance audits against institutionally accepted security controls.}
      \resumeItemListEnd

    \resumeSubheading
      {Kappa Sigma - Cal Poly San Luis Obispo}{San Luis Obispo, CA}
      {President - Risk Manager}{2021 -- 2024}
      \resumeItemListStart
        \resumeItem{Leadership and Management}
          {Worked in coordinating an executive committee to head and direct community service, fundraising, and philanthropy events.}
        \resumeItem{Event Planning and Coordination}
          {Lead and facilitate all chapter executive meetings, and chapter meetings, attend national events, and coordination with other fraternities on campus.}
        \resumeItem{Financial Oversight}
          {Collaborated with the treasurer to manage the chapter's budget.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{IP Blocklist Automation}{Created an automation playbook that streamlines the process of managing a block list from a 3rd party service using Splunk and Splunk SOAR.}
    \resumeSubItem{HomeLab}{Configured a home server using Plex, Bitwarden, WireGuard, and Grafana with Docker.}
    \resumeSubItem{Card Trading Business Database Design with MySQL}{Collaborated on designing and implementing a database system for 'Select \& Collect Cards,' a chain of trading card game stores, focusing on inventory, sales, and customer data management to streamline operations and enhance traceability.}
    \resumeSubItem{Portfolio Website}{Built a personal website using JavaScript, HTML and CSS.  }
  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------------
\section{Campus Involvement and Volunteer Work}
  \resumeSubHeadingListStart
    \resumeCampusInvolvement{Kappa Sigma}{President}{\textit{\small Dec 2022} -- \textit{\small Mar 2023} (President), \textit{\small Sept 2021} -- \textit{\small Present} (Risk Manager)}    
    \resumeCampusInvolvement{Cal Poly Club Baseball Team}{Player}{\textit{\small Sept 2023} -- \textit{\small Current}}
    \resumeCampusInvolvement{Bandit-LLC}{Part Owner}
    {\textit{\small Oct 2024} -- \textit{\small Current}}
  \resumeSubHeadingListE 
%--------PROGRAMMING SKILLS------------
\section{Skills}

\textbf{Languages:} Python, SQL, Java, TypeScript, Splunk Soar Environment\\
\textbf{Skills:} Next.js, Node.js, Docker, Supabase, Six Sigma, LEAN Manufacturing, Splunk, Excel, Linux, git, Slack, SOLIDWORKS, Minitab, Jira  \\


%-------------------------------------------
\end{document}
