%-------------------------
% Nicolo DiFerdinando Resume
% Tailored for Apple IS&T Early Career
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\Huge \scshape Nicolo DiFerdinando} \\ \vspace{3pt}
  \href{mailto:ndiferdi@calpoly.edu}{ndiferdi@calpoly.edu} $|$
  \small 949-274-0390 $|$
  \href{https://www.nicolod.org}{nicolod.org} $|$
  \href{https://www.linkedin.com/in/nicolo-diferdinando/}{linkedin.com/in/nicolo-diferdinando} $|$
  \href{https://github.com/nicodiferd}{github.com/nicodiferd}
\end{center}

%-----------ABOUT ME-----------------
\section{About Me}
\small{Industrial engineering student with experience in full-stack development, cybersecurity automation, and business intelligence. Focused on building internal tools that streamline workflows, designing data pipelines, and solving systems-level problems. CompTIA Security+ and Splunk Core certified.}

%-----------EDUCATION-----------------
\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{California Polytechnic State University, San Luis Obispo} & San Luis Obispo, CA \\
      \textit{\small Bachelor of Science in Industrial Engineering} & \textit{\small Sept 2021 -- June 2026} \\
    \end{tabular*}\vspace{-2pt}
    {\small \textbf{Coursework:} Data Science, Data Analytics, Data Management \& System Design, Operations Research, Machine Learning, Project management, Product Devolvement, UX optimization}
\end{itemize}

%-----------EXPERIENCE-----------------
\section{Experience}
\begin{itemize}[leftmargin=0.15in, label=\textbullet, itemsep=-2pt]

  % PeopleConnect - Combined entry
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{PeopleConnect} & \textit{\small San Diego / Remote, June 2025 -- Present} \\
    \end{tabular*}\vspace{-3pt}
    
    {\small \textit{Business Intelligence Intern} (Oct 2025 -- Present)}\vspace{-5pt}
    \begin{itemize}[leftmargin=0.2in, label=$\circ$, itemsep=-2pt, topsep=2pt]
      \item \small{\textbf{Dashboard Development:} Build interactive dashboards using Sigma Computing, Tableau, and Snowflake to support decision-making across Growth Operations and Finance teams.}
      \item \small{\textbf{Data Pipeline Engineering:} Develop and monitor data pipelines using dbt semantic layers; troubleshoot nightly ETL jobs across the analytics stack.}
    \end{itemize}\vspace{-3pt}
    
    {\small \textit{Cybersecurity \& IT Intern} (June 2025 -- Sept 2025)}\vspace{-5pt}
    \begin{itemize}[leftmargin=0.2in, label=$\circ$, itemsep=-2pt, topsep=2pt]
      \item \small{\textbf{Bash Automation:} Developed bash scripts automating audit reporting workflows, supporting completion of the company's SOC 2 compliance audit.}
      \item \small{\textbf{Enterprise Security:} Deployed on-demand vulnerability scanning solution for enterprise computers, enabling on-site security assessments.}
    \end{itemize}\vspace{-2pt}

  % SOC Analyst
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{Assistant Student SOC Analyst} -- \textit{Cal Poly ITS} & \textit{\small San Luis Obispo, 2024 -- Present} \\
    \end{tabular*}\vspace{-5pt}
    \begin{itemize}[leftmargin=0.2in, label=$\circ$, itemsep=-2pt, topsep=2pt]
      \item \small{\textbf{Security Automation:} Developed Python Slack application automating SOC workflows including email confirmation, user suppression, and blocking. Integrated Splunk SOAR playbooks with Slack Bolt APIs for real-time incident response.}
      \item \small{\textbf{Incident Handling:} Analyze and respond to suspicious logins, phishing emails, and anomalous network traffic using Splunk Enterprise.}
    \end{itemize}\vspace{-2pt}

  % loanDepot
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{Cyber Security Intern} -- \textit{loanDepot} & \textit{\small Irvine, CA, Summer 2022} \\
    \end{tabular*}\vspace{-5pt}
    \begin{itemize}[leftmargin=0.2in, label=$\circ$, itemsep=-2pt, topsep=2pt]
      \item \small{\textbf{Threat Intelligence:} Supported threat prioritization based on actor-based and behavior/tactic-based intelligence. Assisted SOC and CIRT teams in incident investigations.}
      \item \small{\textbf{Security Compliance:} Performed compliance audits against institutionally accepted security controls and frameworks.}
    \end{itemize}\vspace{-2pt}

\end{itemize}

%-----------PROJECTS-----------------
\section{Projects}
\begin{itemize}[leftmargin=0.15in, label=\textbullet, itemsep=-2pt]
  \item \small{\textbf{Flora -- Senior Capstone (Bloomfilter.ai):} Leading year-long research project improving HCI design for AI agent integration in project management tools, focused on increasing user adoption in enterprise software.}
  \item \small{\textbf{Bandit LLC -- Event Rideshare Startup:} Co-founded and built full-stack iOS app using Swift/SwiftUI, TypeScript/Node.js backend, MongoDB, and Firebase Auth with real-time WebSocket ride tracking. Closed Sept 2025.}
  \item \small{\textbf{HomeLab Infrastructure:} Self-hosted environment on Proxmox with VMs (ClickHouse data warehouse, automation bots) and Docker containers (n8n, Pi-hole, Tailscale) with ZFS storage and Grafana monitoring.}
\end{itemize}

%-----------LEADERSHIP-----------------
\section{Leadership}
\begin{itemize}[leftmargin=0.15in, label=\textbullet, itemsep=-2pt]
  \item \small{\textbf{Cal Poly Club Baseball} -- Co-President (June 2025 -- Present), Player (Sept 2023 -- Present)}
  \item \small{\textbf{Kappa Sigma Fraternity} -- President (Dec 2022 -- Mar 2023), Risk Manager (2021 -- 2024)}
\end{itemize}

%--------SKILLS------------
\section{Skills}
{\small
\textbf{Languages:} Python, SQL, TypeScript, JavaScript, Swift/SwiftUI, Bash, HTML/CSS \\
\textbf{Technologies:} Node.js, React, Next.js, MongoDB, Firebase, Docker, Proxmox, Git, Linux, Splunk, Splunk SOAR, Snowflake, dbt, Tableau, Sigma Computing, GCP, Cloudflare
}

%-------------------------------------------
\end{document}